---
title: "Toccatr Package development"
author: "James Smith, Talisman Therapeutics" 
output: 
  html_document: 
    df_print: paged 
    code_folding: hide 
    code_download: true 
  date: Thu 15 Feb 2024 
---

## Intro

Toccatr to do list

```{r setup, warning=FALSE, message=FALSE}
library(devtools)
library(roxygen2)

library(tidyverse, quietly = TRUE) 
library(janitor, quietly = TRUE) 
library(plotly, quietly = TRUE)
source("//10.0.3.251/Projects/Lab reference/Settings and Scientific Reference/slackrs/core_scripts/neuromuscular_function_1_6.r")

```


Need to add prismy_time for timecourse data and prismy_group for grouped format prism data

Create function for pairing multiple evaluations from same dataset side by side  
Either use pivot wider or: split, rename variables by eval (use index not actual eval num), join by platename_well

#### Assuming your dataframe is called 'iris'
Filtereing for platemap
first_species <- iris[1, "Species"]  # Get the species of the first row
filtered_df <- iris %>%
  filter(Species == first_species)  # Select rows with the same species
  select compound and row col, 
  unique(0)

####  Combine multiple evaluations for one plate

dfcols <- df %>% select(-eval) %>% colnames() 
df <- df %>% 
  #mutate(eval_index = match(eval, unique(eval))) %>% 
  pivot_wider(
    names_from = eval_index, 
    values_from = dfcols
  )
 #colnames(df) <- str_replace(colnames(df), "_1", "")
# removes columns which have identical values  - will also remove nas
df2 <- df2[!duplicated(as.list(df2))]



#### Combine two rows

library(dplyr)

  Create the dataframe
df <- tribble(
  ~a, ~b, ~c, ~d,
  "apple", 1.5, NA, 1,
  "banana", 3, NA, 2,
  "orange", 4, NA, 3,
  "apple", NA, 6, 4,
  "banana", NA, 7, 4,
  "orange", NA, 8, 5
)

  Group by column 'a' and remove NAs for each group
  col_list <- c("b", "c")
df_combined <- df %>%
  group_by(a) %>%
  summarise(across(all_of(collist), ~first(na.omit(.))))
  
  
Old name was Tallyho ( **Tali**sman **H**elp for **O**pera )

```{r}

```

